Data Analysis Expanded

### 2019-08-19 data_analysis/data_analysis_expanded.Rmd
Rdata output added (results not complete)

```{r s3_m1_c}
set.seed(452348)
s3_m1_c <- rre::minimum_subset_distance(list_of_samples[[3]],
                                        partitions = 10,
                                        lambda_vec = seq(500, 600 ,by=5),
                                        multiplier = 2,
                                        c_seq_len = 11,
                                        starts = data.frame(alpha = 0.5143,
                                                            delta = 0.003997))
```
```{r s3_m1_c_print, results = 'asis'}
s3_m1_c %>% report_results_2(., list_of_samples[[3]], report_eta = T)
```
<br><br>

@@

```{r s1_m3_d}
# Feed in more alpha and delta, narrow lambdagrid more.
#s1_m3_d <- rre::gof_criterion(list_of_samples[[1]], 
#                              lambda_vec = seq(505,525,by=2),
#                              multiplier = 100,
#                              c_seq_len = 50,
#                              starts = data.frame(alpha = c(0.1, 0.01, 0.01, 0.001), delta = c(0.1, 0.01, 0.0001, 0.001)))
```
```{r s1_m3_d_print, results = 'asis'}
#s1_m3_d %>% report_results_2(.)
```
<br>
<br>

@@

```{r s2_m3_d}
# Selected lambda was on the edge of previous grid, lets try again:
s2_m3_d <- rre::gof_criterion(list_of_samples[[2]], 
                              lambda_vec = seq(150,300,by=10),
                              multiplier = 100,
                              c_seq_len = 50,
                              starts = big_starts)
```
```{r s2_m3_d_print, results = 'asis'}
s2_m3_d %>% report_results_2(., list_of_samples[[2]], report_eta =T)
```
<br>
<br>

@@

@@

>>>>

```{r s3_m1_d}
set.seed(452348)
s3_m1_d <- rre::minimum_subset_distance(list_of_samples[[3]],
                                        partitions = 10,
                                        lambda_vec = seq(500, 600 ,by=5),
                                        multiplier = 2,
                                        c_seq_len = 11,
                                        starts = data.frame(alpha = 0.5143,
                                                            delta = 0.003997))
```
```{r s3_m1_d_print, results = 'asis'}
s3_m1_d %>% report_results_2(., list_of_samples[[3]], report_eta = T)
```
<br><br>

@@

```{r s1_m3_d}
#s1_m3_d <- rre::gof_criterion(list_of_samples[[1]], 
#                              lambda_vec = seq(450,550,by=10),
#                              multiplier = 200,
#                              c_seq_len = 200,
#                              starts = data.frame(alpha = 0.001738,
#                                                  delta = 0.001744))
```
```{r s1_m3_d_print, results = 'asis'}
#s1_m3_d %>% report_results_2(., list_of_samples[[1]], report_eta = T)
```
<br><br>
<br><br>

@@

```{r s2_m3_d}
# Selected lambda was on the edge of previous grid, lets try again:
s2_m3_d <- rre::gof_criterion(list_of_samples[[2]], 
                              lambda_vec = seq(150,300,by=10),
                              multiplier = 100,
                              c_seq_len = 50,
                              starts = big_starts)
```
```{r s2_m3_d_print, results = 'asis'}
s2_m3_d %>% report_results_2(., list_of_samples[[2]], report_eta =T)
```
<br><br>

```{r s2_m3_e}
# Selected lambda was on the edge of previous grid, lets try again:
#s2_m3_e <- rre::gof_criterion(list_of_samples[[2]], 
#                              lambda_vec = seq(150,300,by=5),
#                              multiplier = 100,
#                              c_seq_len = 499,
#                              starts = data.frame(alpha = 0.004656,
#                                                  delta = 0.0025668))
```
```{r s2_m3_e_print, results = 'asis'}
#s2_m3_e %>% report_results_2(., list_of_samples[[2]], report_eta =T)
```
<br><br>
<br><br>

@@

```{r s3_m3_e}
# Selected lambda was on the edge of previous grid, lets try again:
#s3_m3_e <- rre::gof_criterion(list_of_samples[[3]], 
#                              lambda_vec = seq(150, 250, by=5),
#                              multiplier = 100,
#                              c_seq_len = 499,
#                              starts = data.frame(alpha = 0.0014137,
 #                                                 delta = 0.001367))
```
```{r s3_m3_e_print, results = 'asis'}
#s3_m3_e %>% report_results_2(., list_of_samples[[3]], report_eta = T)
```
<br><br><br><br>

@@

## Output data

For each method and sample we save the most refined or best estimate.
```{r output_data}
sample_1 <- list(method_0 = s1_m0_b$best,
                 method_1 = s1_m1_d$best,
                 method_2 = s1_m2_b$best,
                 method_3 = s1_m3_c$best,
                 method_4 = s1_m4_b$best)

sample_2 <- list(method_0 = s2_m0_b$best,
                 method_1 = s2_m1_c$best,
                 method_2 = s2_m2_b$best,
                 method_3 = s2_m3_d$best,
                 method_4 = s2_m4_b$best)

sample_3 <- list(method_0 = s3_m0_b$best,
                 method_1 = s3_m1_d$best,
                 method_2 = s3_m2_b$best,
                 method_3 = s3_m3_d$best,
                 method_4 = s3_m4_b$best)

sample_outputs <- list(sample_1 = sample_1, 
                       sample_2 = sample_2, 
                       sample_3 = sample_3)

save(sample_outputs, file = "data_analysis_expanded_results.RData")

```
